Analyzing the impact of social attributes on the success of commit integration

### 2017-02-18 Paper/MSRChallenge2017.tex
removed repeat word

Previous studies have identified a relationship between technical and social 
factors and pull request acceptance. We are interested in understanding if
social factors, that proxy experience, can be used to predict a
a different success measure: continuous integration success.

>>>>

Previous studies have identified a relationship between technical and social 
factors and pull request acceptance. We are interested in understanding if
social factors, that proxy experience, can be used to predict
a different success measure: continuous integration success.
